Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Update paper.tex
Amend the CCS BS to look more official and correct

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  [REWRITE THIS AT END]
  The growth of online video games has yielded a vast underground economy of
  criminals who sell exploits and credentials to give gamers unfair advantages
  in the games. This paper studies the sale of ``crimeware'' connected to
  the Epic Games' ``Fortnite: Battle Royale'' video game. The authors created 
  a webscraping tool to collect large amounts of data from a hacker forum to 
  analyze key distributers in the economy. After analyzing approximately 7000
  comments and 113 threads posted on the forum, the authors found that 
  crimeware called "Aimbots" and the CaaS (Crimeware-as-a-Service) "Account Sales"
  were the most common things for sale in the Hack Forums marketplaces. The 
  authors propose several solutions that the developers can implement to 
  combat the proliferation of underground economy dealing in Fortnite exploits.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
% i never got this to work
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

@@

\begin{figure}
	\centering
	\includegraphics[width = .5\linewidth]{DylanProduct.png}
	\caption{Dylan's Product Advertisement}
\end{figure}

@@

%[A table would be a nice addition here]
%[DISCUSS THE DIFFERENT KEY MEMBERS OF THE COMMUNITY]
%[WHICH CHEATS ARE MOST POPULAR]

@@

\subsection{Account Theft}
% [MFA (already in Fortnite) but suggest mandating it]
Given the prominence of account theft and sales, we propose that Fortnite -
and other online video games like it - mandate the use of multi-factor
authentication (MFA) in combination with username and password credentials to
secure accounts. Epic Games has already implemented an MFA tool for players to 
use to protect their accounts, and the game incentivizes players to use it;
however, we argue that optional usage of MFA is insufficient, and that online 
video game developers should require the usage of MFA as part of accessing one's
account. Additionally, we suggest that video game developers create their own 
solution instead of relying on a simple SMS numerical code. SMS messages can be 
intercepted, and an attacker can actually acquire the code for login. However,
a robust, novel implementation can likely thwart the majority of hackers and 
provide for the safety of a user's account.

% [FIND STATS OF HOW IT REDUCES BREACHES]
% https://security.googleblog.com/2019/05/new-research-how-effective-is-basic.html

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  The growth of online video games has yielded a vast underground economy of
  criminals who sell exploits and credentials to give gamers unfair advantages
  in the games. This paper studies the sale of ``crimeware'' connected to
  the Epic Games' ``Fortnite: Battle Royale'' video game. The authors created 
  a webscraping tool to collect large amounts of data from a hacker forum to 
  analyze key distributers in the economy. After analyzing approximately 7000
  comments and 113 threads posted on the forum, the authors found that 
  crimeware called "Aimbots" and the CaaS (Crimeware-as-a-Service) "Account Sales"
  were the most common things for sale in the Hack Forums marketplaces. The 
  authors propose several solutions that the developers can implement to 
  combat the proliferation of underground economy dealing in Fortnite exploits.
\end{abstract}

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10002951.10003260.10003277.10003279.10010847</concept_id>
  <concept_desc>Information systems~Surfacing</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10010405.10010462.10010465</concept_id>
  <concept_desc>Applied computing~Evidence collection, storage and analysis</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10010147.10010257.10010293.10003660</concept_id>
  <concept_desc>Computing methodologies~Classification and regression trees</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Surfacing}
\ccsdesc[500]{Applied computing~Evidence collection, storage and analysis}
\ccsdesc[300]{Computing methodologies~Classification and regression trees}

@@

\begin{figure}
	\centering
	\includegraphics[width = .5\linewidth]{DylanProduct.png}\cite{opium}
	\caption{Dylan's Product Advertisement}
\end{figure}

@@

@@

\subsection{Account Theft}
Given the prominence of account theft and sales, we propose that Fortnite -
and other online video games like it - mandate the use of multi-factor
authentication (MFA) in combination with username and password credentials to
secure accounts. Epic Games has already implemented an MFA tool for players to 
use to protect their accounts, and the game incentivizes players to use it;
however, we argue that optional usage of MFA is insufficient, and that online 
video game developers should require the usage of MFA as part of accessing one's
account. According to a study from Google, adding a recovery phone number 
reduced the prevented "100\% of automated bots, 99\% of bulk phishing attacks, 
and 66\% of targeted attacks" in their study" \cite{google}. Although this 
study is specific to Google's implementations and security policies, it is a 
valuable heuristic to show how multi-factor authentication can greatly bolster
security for a user.

Additionally, we suggest that video game developers create their own 
solution instead of relying on a simple SMS numerical code. SMS messages can be 
intercepted, and an attacker can actually acquire the code for login. However,
a robust, novel implementation can likely thwart the majority of hackers and 
provide for the safety of a user's account.
